---
title: "Statistical Inference Part 2"
author: "Viktor M"
date: "Thursday, April 24, 2015"
output: pdf_document
---

[My github page](https://github.com/dainova/6_Statistical_Inference)

<h4>Synopsis</h4>

In this research we will analyze the ToothGrowth data in the R datasets package.

<br><br>  


  
<h5>Here we assign all variables and prepare data set to be used in our research</h5> 

```{r}
data(ToothGrowth)
ToothGrowth$dose<-as.factor(ToothGrowth$dose)
head(ToothGrowth,3)
str(ToothGrowth)
```


<h5> Create basic plot using lattice package</h5> 
```{r}
library(lattice)
xyplot(len~dose|supp, ToothGrowth,
       main="Scatterplots by supplement type and dose", 
       ylab="Length", xlab="Dose")
```
<br><br>

<h5> Create boxplot</h5> 
```{r}
boxplot(len ~ supp * dose,ToothGrowth, 
        col="lightgreen", ylab="Length", xlab="Type & Dose",main="Boxplots by Type and Dow")
```
As we can observe OJ promotes better tooghgrowth comparing to VC.
<br><br>


<h5> Show basic structrue and summary for all data</h5> 
```{r}
summary(ToothGrowth)
```
<br>

<h5> And show it for each of categories we researched</h5> 
```{r}
summary(ToothGrowth[ToothGrowth$supp=="OJ",])
```
<h5> And show it for each of categories we researched</h5> 
```{r}
summary(ToothGrowth[ToothGrowth$supp=="VC",])
```
<br><br>

  
  
<h5> Now we will compare growth dynamics by categories using Confidence intervals and Hypythesis</h5> 
First for supp :
```{r}
t.test(len ~supp,ToothGrowth[ToothGrowth$dose==0.5,],paired=FALSE, var.equal=TRUE)
``` 
Using t.test with dose=0.5  we observe that OJ performs bettter then VC.
<br>
  
  
```{r}
t.test(len ~supp,ToothGrowth[ToothGrowth$dose==1,],paired=FALSE, var.equal=TRUE)
```
Using t.test with dose=1  we observe that results are opposite.
<br>
  
  
```{r}
t.test(len ~supp,ToothGrowth[ToothGrowth$dose==2,],paired=FALSE, var.equal=TRUE)
```
And for dose=2  there are not significant difference.

<br><br>

And for len

```{r}
t.test(len ~dose,ToothGrowth[ToothGrowth$dose!=0.5,],paired=FALSE, var.equal=TRUE)
```  

```{r}
t.test(len ~dose,ToothGrowth[ToothGrowth$dose!=2,],paired=FALSE, var.equal=TRUE)
```    
<br><br>

 <h4>Conclusion</h4>

 Assuming that each Guinea pig treated with suppliment type and dosage randomly assigned and 60 head cound can represent of all its population we ca state that:
 1. Supplement type doesn't have any effect on tooth growth.
 2. Increasing the dose level promotes  tooth growth.

